Legacy Data Confounds Genomics Studies

### 2019-07-12 LatexManuscript/legacy.tex
update figure S4

\caption{Comparing results from the single population tests, we find 812 variants independently associated with average quality of mapped bases $Q$ in more than one population.
\textbf{A} For each population, we plot the number of variants associated to at least one other population.
\textbf{B} The number of populations for which a variant has reached significance.}
  \label{OverLap}
\end{figure}

>>>>

\caption{Comparing results from the single population tests, we find 812 variants that pass the strict mask that are independently associated with average quality of mapped bases $Q$ in more than one population.
\textbf{A} For each population, we plot the number of variants associated to at least one other population.
Phase 1 populations are indicated with a star (*).
\textbf{B} The number of populations for which a variant has reached significance. Many of the variants associated in only one population do not pass the strict mask. }
  \label{OverLap}
\end{figure}
